\textbf{skater}: An R package for SNP-based Kinship Analysis, Testing, and Evaluation

### 2022-01-12 paper/paper.tex
figure caption

\textbf{skater package version}: 0.1.0

@@

\begin{center}\includegraphics{paper_files/figure-latex/plotped-1} \end{center}

@@

\begin{verbatim}
## # A tibble: 288 x 6
##    fid      id1               id2                   k degree_truth degree_inferred
##    <chr>    <chr>             <chr>             <dbl> <chr>        <chr>          
##  1 testped1 testped1_g1-b1-s1 testped1_g1-b1-s1 0.5   0            0              
##  2 testped1 testped1_g1-b1-i1 testped1_g1-b1-s1 0     unrelated    unrelated      
##  3 testped1 testped1_g1-b1-s1 testped1_g2-b1-s1 0     unrelated    unrelated      
##  4 testped1 testped1_g1-b1-s1 testped1_g2-b1-i1 0.25  1            1              
##  5 testped1 testped1_g1-b1-s1 testped1_g2-b2-s1 0     unrelated    unrelated      
##  6 testped1 testped1_g1-b1-s1 testped1_g2-b2-i1 0.25  1            1              
##  7 testped1 testped1_g1-b1-s1 testped1_g3-b1-i1 0.125 2            2              
##  8 testped1 testped1_g1-b1-s1 testped1_g3-b2-i1 0.125 2            1              
##  9 testped1 testped1_g1-b1-i1 testped1_g1-b1-i1 0.5   0            0              
## 10 testped1 testped1_g1-b1-i1 testped1_g2-b1-s1 0     unrelated    unrelated      
## # ... with 278 more rows
\end{verbatim}

@@

\begin{verbatim}
## $Accuracy
## # A tibble: 1 x 5
##   Accuracy `Accuracy LL` `Accuracy UL` `Accuracy Guessing` `Accuracy P-value`
##      <dbl>         <dbl>         <dbl>               <dbl>              <dbl>
## 1    0.812         0.763         0.856               0.333           1.09e-62
## 
## $Other
## # A tibble: 6 x 15
##   Class         N `Sensitivity/Re~ `Specificity/TN~ `PPV/Precision`   NPV `F1/Dice`
##   <chr>     <dbl>            <dbl>            <dbl>           <dbl> <dbl>     <dbl>
## 1 0          64              0.75             0.964           0.857 0.931     0.8  
## 2 1          72              0.806            0.944           0.829 0.936     0.817
## 3 2          48              0.833            0.967           0.833 0.967     0.833
## 4 3           8              0.75             0.936           0.25  0.992     0.375
## 5 unrelated  96              0.854            0.958           0.911 0.929     0.882
## 6 Average    57.6            0.799            0.954           0.736 0.951     0.741
## # ... with 8 more variables: Prevalence <dbl>, Detection Rate <dbl>,
## #   Detection Prevalence <dbl>, Balanced Accuracy <dbl>, FDR <dbl>, FOR <dbl>,
## #   FPR/Fallout <dbl>, FNR <dbl>
## 
## $Table
##            Target
## Predicted    0  1  2  3 unrelated
##   0         48  4  2  1         1
##   1          5 58  4  0         3
##   2          0  3 40  1         4
##   3          8  4  0  6         6
##   unrelated  3  3  2  0        82
## 
## $recip_rmse
## [1] 0.4665971
\end{verbatim}

>>>>

\textbf{skater package version}: 0.1.1

@@

\begin{figure}

{\centering \includegraphics{paper_files/figure-latex/plotped-1}

}

\caption{Pedigree diagram for the first family in the pedigree shown in the code above.}\label{fig:plotped}
\end{figure}

@@

\begin{verbatim}
## # A tibble: 288 x 6
##    fid      id1               id2                 k degree_truth degree_inferred
##    <chr>    <chr>             <chr>           <dbl> <chr>        <chr>          
##  1 testped1 testped1_g1-b1-s1 testped1_g1-b1~ 0.5   0            0              
##  2 testped1 testped1_g1-b1-i1 testped1_g1-b1~ 0     unrelated    unrelated      
##  3 testped1 testped1_g1-b1-s1 testped1_g2-b1~ 0     unrelated    unrelated      
##  4 testped1 testped1_g1-b1-s1 testped1_g2-b1~ 0.25  1            1              
##  5 testped1 testped1_g1-b1-s1 testped1_g2-b2~ 0     unrelated    unrelated      
##  6 testped1 testped1_g1-b1-s1 testped1_g2-b2~ 0.25  1            1              
##  7 testped1 testped1_g1-b1-s1 testped1_g3-b1~ 0.125 2            2              
##  8 testped1 testped1_g1-b1-s1 testped1_g3-b2~ 0.125 2            1              
##  9 testped1 testped1_g1-b1-i1 testped1_g1-b1~ 0.5   0            0              
## 10 testped1 testped1_g1-b1-i1 testped1_g2-b1~ 0     unrelated    unrelated      
## # ... with 278 more rows
\end{verbatim}

@@

\begin{verbatim}
## $Accuracy
## # A tibble: 1 x 5
##   Accuracy `Accuracy LL` `Accuracy UL` `Accuracy Guessing` `Accuracy P-value`
##      <dbl>         <dbl>         <dbl>               <dbl>              <dbl>
## 1    0.812         0.763         0.856               0.333           1.09e-62
## 
## $Other
## # A tibble: 6 x 15
##   Class      N `Sensitivity/Re~ `Specificity/TN~ `PPV/Precision`   NPV `F1/Dice`
##   <chr>  <dbl>            <dbl>            <dbl>           <dbl> <dbl>     <dbl>
## 1 0       64              0.75             0.964           0.857 0.931     0.8  
## 2 1       72              0.806            0.944           0.829 0.936     0.817
## 3 2       48              0.833            0.967           0.833 0.967     0.833
## 4 3        8              0.75             0.936           0.25  0.992     0.375
## 5 unrel~  96              0.854            0.958           0.911 0.929     0.882
## 6 Avera~  57.6            0.799            0.954           0.736 0.951     0.741
## # ... with 8 more variables: Prevalence <dbl>, Detection Rate <dbl>,
## #   Detection Prevalence <dbl>, Balanced Accuracy <dbl>, FDR <dbl>, FOR <dbl>,
## #   FPR/Fallout <dbl>, FNR <dbl>
## 
## $Table
##            Target
## Predicted    0  1  2  3 unrelated
##   0         48  4  2  1         1
##   1          5 58  4  0         3
##   2          0  3 40  1         4
##   3          8  4  0  6         6
##   unrelated  3  3  2  0        82
## 
## $recip_rmse
## [1] 0.4665971
\end{verbatim}
